### 2019-03-14 proposals/TESS_GI_cycle02/tessgi_gully_cycle2.tex
Start putting the outline into the proposal

\begin{center}
\bfseries\uppercase{%
%%
%% ENTER TITLE OF PROPOSAL BELOW THIS LINE
REPLACE THIS LINE WITH THE TITLE
%%
%%
}
\end{center}

@@

\noindent{The recommended sections for a TESS GI proposal are shown below. Feel free to change section
headings as necessary, but this is the suggested minimal information that should be included in the proposal.
This Science/Technical section of the proposal is limited to 4 pages including figures and references.}

@@

Provide text and figures that justify the scientific need for \tess\ observations and analyses here.
Justify your choice of cadence. When applicable, justify your choice of new 2 min cadence observations.
If your program includes theoretical, simulation, or ground-based observing components (limited to no
more than 30\% effort), describe why these efforts are critical in addition to \tess\ observations.

@@

\subsection{({\it Only} For ToO Proposals) Trigger Criteria}

If the proposed investigation includes Targets of Opportunity (ToO's), describe also the circumstances
under which a ToO is triggered, an estimated duration of the event(s), and an estimated probability for
triggering the observations. Also discuss the potential science impact imposed by the delay in upload
of the event due to \tess\ orbit/uplink constraints.

@@

Discuss how you plan to analyze the \tess\ data. This includes the development of software tools.

@@

Provide text and figures showing that the proposed \tess\ investigations are feasible; consider the
\tess\ survey strategy, target observability, and required signal-to-noise, etc. The \tess\ Science
Support Center (\href{https://heasarc.gsfc.nasa.gov/docs/tess/}{TSSC}) makes several tools available to help estimate these quantities.

>>>>

\begin{center}
\bfseries\uppercase{%
%%
%% ENTER TITLE OF PROPOSAL BELOW THIS LINE
Starspots confound derived stellar properties and a concept for probabilistic mitigation
%%
%%
}
\end{center}

@@

@@

\subsection{Starspots as confounders of isochronal ages}
Provide text and figures that justify the scientific need for \tess\ observations and analyses here.
Justify your choice of cadence. When applicable, justify your choice of new 2 min cadence observations.
If your program includes theoretical, simulation, or ground-based observing components (limited to no
more than 30\% effort), describe why these efforts are critical in addition to \tess\ observations.

@@

\subsection{Transit light source effect}
thinga

\subsection{Stellar surface structures as a gateway for brown dwarf cloud modelin}
more yjumd

@@

\subsection{Get amplitudes and periods for a large fraction of stars from TESS data}
\subsection{Get starspot temperature and coverage fraction for a sample of these stars from spectroscopy}
\subsection{Compute the ratio of TESS amplitude to total spot coverage}
\subsection{Compute a regression of spot coverage to rotation rate and spectral subtype.}

@@

\subsection{Essentially measuring periods and amplitudes, which has been demonstrated}
\subsection{There will be enough GKM stars}
\subsection{The TESS precision will be adequate}
\subsection{I have already applied the spectral technique to a wide range of young stars}
\subsection{Availability of archival spectroscopy}
